NumPy---Array Programming in Python

### 2020-02-04 body.tex
Update caption

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{Scientific Python Ecosystem.}
   This figure highlights just a few of the essential tools and libraries in the vast
   scientific Python ecosystem.  Most of the ecosystem builds on NumPy arrays to
   provide a rich and powerful collection of array-aware functionality.
   This means that other array implementations are easily accessible to
   the ecosystem if they use the NumPy API and array protocol (Fig.~\ref{fig:array-protocol}).
  }
  \label{fig:ecosystem}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{Scientific Python Ecosystem.}
   This figure highlights some of the essential tools and libraries, which depend
   on NumPy.  Since most of the ecosystem
   builds on NumPy arrays and its rich and powerful collection of array-aware
   functionality, the simplest way for other array implementations to become
   available to the vast scientific Python ecosystem is by using the NumPy API and array
   protocols (Fig.~\ref{fig:array-protocol}).
  }
  \label{fig:ecosystem}
\end{figure}
